Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-13 doc/camera-ready/paper.tex
typo
Edit of last paragraph

\paragraph{Collecting rewards.}
$\Q_{reward}$ contains instances where  an agent needs to navigate a rectangular
grid to pick up  rewards spread on the grid  while 
avoiding \emph{blocked} cells. This is  variation of an
example  by \citeay{garnelo2016towards}.
The STRIPS instances have the primitive predicates $reward(\cdot)$, $at(\cdot)$, $blocked(\cdot)$
and $adjacent(\cdot,\cdot)$ that denote the position of the rewards, of
the agent, of the blocked cells, and the grid topology respectively.
Pipeline 1--6  is fed with two instances of the problem of sizes $4 \times 4$
and $5\times 5$, and having different distributions of blocked cells and rewards.
Two numerical features are learned:
\begin{enumerate}[--]
  \item $R: \abs{reward}$ (number of remaining rewards), 
  \item $D:\! dist(at, adjacent{:}\neg blocked, reward)$ (distance from current
    cell to closest cell with reward, traversing adjacent, unblocked cells only).
\end{enumerate}
The learned set of abstract actions is:
\begin{enumerate}[--]
  \item $\text{collect-reward} = \abst{D=0, R > 0}{R\mminus, D\pplus}$,
  \item $\text{move-to-closest-reward} = \abst{R>0, D>0}{D\mminus}$.
\end{enumerate}

@@

Finally, problems involving non-deterministic transitions may be
accommodated with a simple fix to the SAT theory.
It would be enough to replace the formula \eqref{eq:bridge1} that
links $D1$ and $D2$ with a formula that says that when $s$ and $t$ are
indistinguishable (i.e.\ $\neg D1(s,t)$), for each action $a$ on $s$,
there is an action $b$ on $t$ whose transitions are indistinguishable
from those of $a$ on $s$. To do this, transitions $(s,s')$ in the sample
would need to be tagged with action labels as $(s,a,s')$.

>>>>

\paragraph{Collecting rewards.}
$\Q_{reward}$ contains instances where  an agent needs to navigate a rectangular
grid to pick up  rewards spread on the grid  while 
avoiding \emph{blocked} cells. This is a variation of an
example  by \citeay{garnelo2016towards}.
The STRIPS instances have the primitive predicates $reward(\cdot)$, $at(\cdot)$, $blocked(\cdot)$
and $adjacent(\cdot,\cdot)$ that denote the position of the rewards, of
the agent, of the blocked cells, and the grid topology respectively.
Pipeline 1--6  is fed with two instances of the problem of sizes $4 \times 4$
and $5\times 5$, and having different distributions of blocked cells and rewards.
Two numerical features are learned:
\begin{enumerate}[--]
  \item $R: \abs{reward}$ (number of remaining rewards), 
  \item $D:\! dist(at, adjacent{:}\neg blocked, reward)$ (distance from current
    cell to closest cell with reward, traversing adjacent, unblocked cells only).
\end{enumerate}
The learned set of abstract actions is:
\begin{enumerate}[--]
  \item $\text{collect-reward} = \abst{D=0, R > 0}{R\mminus, D\pplus}$,
  \item $\text{move-to-closest-reward} = \abst{R>0, D>0}{D\mminus}$.
\end{enumerate}

@@

Finally, problems involving non-deterministic transitions may be
accounted for with a simple change to the SAT theory.
It would be sufficient to replace the formula \eqref{eq:bridge1}
that links $D1$ and $D2$ with a formula that establish that when
$s$ and $t$ are indistinguishable (i.e.\ $\neg D1(s,t)$), then
for each action $a$ on $s$, there is an action $b$ on $t$ whose
set of transitions from $t$ are indistinguishable from the set
of transitions of $a$ on $s$.
To do this, transitions $(s,s')$ in the sample would need to be
tagged with action labels as $(s,a,s')$.
